\documentclass[margin,line,11pt,letterpaper]{style}

    \usepackage[colorlinks=false]{hyperref}
    \hypersetup{
        colorlinks=false,
        linkcolor=blue,
        filecolor=magenta,      
        urlcolor=cyan,
    }

    % Side section header styling
    \let\oldsection\section
    \renewcommand{\section}[1]{\vspace{-2mm}\oldsection{\small\sc {#1}}}
    
\begin{document}
\newsectionwidth{1in}

\name{\makebox[\resumewidth]{{\LARGE Alexander Sedgwick Aubuchon} \hfill}}

\address{}

\begin{resume}
    \vspace{-9mm}
    \section{Contact Information}
    Mail: \href{mailto:alex@aub.dev}{alex@aub.dev} \hfill GitHub: \url{https://github.com/reasonablytall}\\
    Phone: +1 (978) 894-6108 \hfill LinkedIn: \url{https://linkedin.com/in/reasonablytall}
    
    
    \section{Education}
    
    \begin{format}
        \employer{l}\location{r}\\
        \title{l}\dates{r}\\
        \body\\
    \end{format}
    
    \employer{\textbf{Northeastern University}}
    \title{\textit{BS in Computer Science, 3.9/4.0 GPA}}
    \dates{\textit{September 2015 - Dec 2019}}
    \location{Boston, MA}
    \begin{position}
        \vspace{-4mm}\\
        Coursework: Advanced Algorithms, Networks, Theory of Comp., NLP, Quantum Mechanics
    \end{position}
    
    \section{Work Experience}
    
    \employer{\textbf{Stripe}}
    \title{\textit{Software Engineer Intern, Orchestration Team}}
    \dates{\textit{January 2020 - April 2020}}
    \location{San Francisco, CA}
    \begin{position}
        \vspace{-4mm}\\
        \emph{Golang, Kubernetes}
        \begin{list2}
            \item Built instance autoscaling for our Kubernetes cluster saving \$1MM per year and significantly reducing infrastructure toil for product teams.
        \end{list2}
    \end{position}
    
    \vspace{-1mm}
    \employer{\textbf{Google}}
    \title{\textit{Software Engineer Intern, Node.js Team}}
    \dates{\textit{May 2019 - August 2019}}
    \location{Sunnyvale, CA}
    \begin{position}
        \vspace{-4mm}\\
        \emph{Node.js, Typescript, C++}
        \begin{list2}
            \item Made contributions to Node.js core and prototyped a faster Node.js dependency loader.
            \item Worked on API design of ESM Loader Hooks in Node.js core.
        \end{list2}
    \end{position}
    
    \vspace{-1mm}
    \employer{\textbf{ASICS Digital}}
    \title{\textit{Data Engineer Coop, Platforms}}
    \dates{\textit{January 2019 - May 2019}}
    \location{Boston, MA}
    \begin{position}
        \vspace{-4mm}\\
        \emph{Python, SQL, AWS, Terraform}
        \begin{list2}
            \item Diagnosed and mitigated urgent data collection breakages. 
            \item Made significant automation and diagnostic improvements to AWS based ETL pipelines.
        \end{list2}
    \end{position}

    \vspace{-1mm}
    \employer{\textbf{CERN, Compact Muon Solenoid}}
    \title{\textit{Software Engineer \& Data Analyst Coop, EMTF}}
    \dates{\textit{January 2018 - August 2018}}
    \location{Geneva, Switzerland}
    \begin{position}
        \vspace{-4mm}\\
        \emph{Python, React, Docker, OpenStack, C++, ROOT}
        \begin{list2}
            \item Built a platform for statistical tests comparing data quality between accelerator runs.
            \item Analyzed EMTF data and predicted post HL-LHC detector performance.
        \end{list2}
    \end{position}

    \vspace{-1mm}
    \employer{\textbf{Draper Laboratories}}
    \title{\textit{Software Engineer Coop, Machine Intelligence}}
    \dates{\textit{January 2017 - August 2017}}
    \location{Cambridge, MA}
    \begin{position}
        \vspace{-4mm}\\
        \emph{C\#, Python, Matlab}
        \begin{list2}
            \item Implemented the USB software interface to a neuro-stimulation experimentation device.
            \item Performed research into the novel uses of RF sensors on the emissions of electronic devices.
        \end{list2}
    \end{position}
    
    \vspace{-1mm}
    \employer{\textbf{MIT Media Lab}}
    \title{\textit{Assistant Researcher, Changing Places}}
    \dates{\textit{July 2016 - January 2018}}
    \location{Cambridge, MA}
    \begin{position}
        \vspace{-4mm}\\
        \emph{Python, scikit, C\#, Unity}
        \begin{list2}
            \item Developed ML models and Unity/C\# worlds for quickly predicting and displaying the traffic and solar potential of a model city.
        \end{list2}
    \end{position}

    \section{Publications}
    
    \begin{format}
        \title{l}\\
        \employer{l}\\
    \end{format}
    
    \title{\textbf{Classification of Electronic Devices and Software Processes via Unintentional Electronic Emissions With Neural Decoding Algorithms} | \href{https://ieeexplore.ieee.org/document/8674781}{link} | \textit{March 2019}}
    \dates{\textit{March 2019}}
    \employer{\textit{Laura J. Mariano, Alexander Aubuchon, Troy Lau, Onur Ozdemir, Tomo Lazovich, John Coakley}}
    \begin{position}
    \end{position}
    
    \vspace{-1mm}
    \title{\textbf{Real-time Machine Learning Prediction of an Agent-Based Model for Urban Decision-making (Extended Abstract)} | \href{https://dl.acm.org/citation.cfm?id=3238109}{link} | \textit{July 2018}}
    \dates{\textit{September 2017}}
    \employer{\textit{Yan Zhang, Arnaud Grignard, Kevin Lyons, Alexander Aubuchon, Kent Larson}}
    \begin{position}
    \end{position}
    
    \section{Computer Skills}
    \renewcommand{\linespread}{5}
    \textbf{Extensive:} Linux, Git, Golang, Rust, Python, Typescript \\
    \textbf{Versed:} \LaTeX, C, C++, Lisp, Node.js, React
     
    \section{Interests}
    Gaming; Rock Climbing; Electronics
\end{resume}
\end{document}
